Analysis of Retrospective COVID-19 data

### 2020-10-22 manuscript/analysis_brms.Rmd
Minor tweaks to brms analysis

cache_dir <- here::here("local_temp_data")
if (!dir.exists(cache_dir)) {
  dir.create(cache_dir)
}
```

@@

dummy_coding <- function(x, lvls = levels(x)) {
  x <- factor(x, levels = lvls)
  contrasts(x) <- contr.treatment(levels(x))
  x
}
```

@@

fit_survival_base <- brm(
  formula = form_survival_base,
  data = data$patient_data,
  prior = prior_survival_base,
  file = paste0(cache_dir, "/fit_survival_base")
)
fit_survival_base <- add_criterion(fit_survival_base, "loo")
```

@@

```{r}
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r, results="hide"}
fit_survival_base_7 <- brm(
  formula = form_survival_base,
  data = data$surv_data_7,
  prior = prior_survival_base,
  file = paste0(cache_dir, "/fit_survival_base_7")
)
fit_survival_base_7 <- add_criterion(fit_survival_base_7, "loo")
```

@@

```{r, results="hide"}
fit_survival_base_28 <- brm(
  formula = form_survival_base,
  data = data$surv_data_28,
  prior = prior_survival_base,
  file = paste0(cache_dir, "/fit_survival_base_28")
)
fit_survival_base_28 <- add_criterion(fit_survival_base_28, "loo")
```

@@

fit_survival_time <- brm(
  formula = form_survival_time,
  data = data$surv_data_last_day,
  prior = prior_survival_time,
  inits = 0,
  file = paste0(cache_dir, "/fit_survival_time")
)
fit_survival_time <- add_criterion(fit_survival_time, "loo")
```

@@

fit_discharged_base <- brm(
  formula = form_discharged_base,
  data = data$patient_data,
  prior = prior_discharged_base,
  file = paste0(cache_dir, "/fit_discharged_base")
)
fit_discharged_base <- add_criterion(fit_discharged_base, "loo")
```

@@

```{r, results="hide"}
fit_discharged_base_7 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_7,
  prior = prior_discharged_base,
  file = paste0(cache_dir, "/fit_discharged_base_7")
)
fit_discharged_base_7 <- add_criterion(fit_discharged_base_7, "loo")
```

@@

```{r, results="hide"}
fit_discharged_base_28 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_28,
  prior = prior_discharged_base,
  file = paste0(cache_dir, "/fit_discharged_base_28")
)
fit_discharged_base_28 <- add_criterion(fit_discharged_base_28, "loo")
```

@@

fit_discharged_time <- brm(
  formula = form_discharged_time,
  data = data$surv_data_last_day,
  prior = prior_discharged_time,
  inits = 0,
  control = list(adapt_delta = 0.95),
  file = paste0(cache_dir, "/fit_discharged_time")
)
fit_discharged_time <- add_criterion(fit_discharged_time, "loo")
```

@@

fit_outcome_base <- brm(
  formula = form_outcome_base,
  data = data$patient_data,
  prior = prior_outcome_base,
  file = paste0(cache_dir, "/fit_outcome_base")
)
fit_outcome_base <- add_criterion(fit_outcome_base, "loo")
```

@@

```{r, results="hide"}
fit_outcome_base_7 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_7,
  prior = prior_outcome_base,
  file = paste0(cache_dir, "/fit_outcome_base_7")
)
fit_outcome_base_7 <- add_criterion(fit_outcome_base_7, "loo")
```

@@

```{r, results="hide"}
fit_outcome_base_28 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_28,
  prior = prior_outcome_base,
  file = paste0(cache_dir, "/fit_outcome_base_28")
)
fit_outcome_bas_28 <- add_criterion(fit_outcome_base_28, "loo")
```

@@

fit_worst_breathing_base <- brm(
  formula = form_worst_breathing_base,
  data = data$patient_data,
  prior = prior_worst_breathing_base,
  file = paste0(cache_dir, "/fit_worst_breathing_base")
)
fit_worst_breathing_base <- add_criterion(fit_worst_breathing_base, "loo")
```

@@

```{r}
hypothesis_res_all <- do.call(rbind, hypothesis_res_list)
write_csv(hypothesis_res_all, path = paste0(cache_dir, "/analysis_brms.csv"))
```

>>>>

cache_dir <- here::here("local_temp_data", "analysis_brms")
if (!dir.exists(cache_dir)) {
  dir.create(cache_dir, recursive = TRUE)
}
```

@@

dummy_coding <- function(x, lvls = levels(x)) {
  x <- factor(x, levels = lvls)
  contrasts(x) <- contr.treatment(levels(x))
  x
}

default_control <- list(adapt_delta = 0.95)
```

@@

fit_survival_base <- brm(
  formula = form_survival_base,
  data = data$patient_data,
  prior = prior_survival_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_base")
)
fit_survival_base <- add_criterion(fit_survival_base, "loo")
```

@@

```{r}
#Marking the results as suspicious because there was a divergence...
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r, results="hide"}
fit_survival_base_7 <- brm(
  formula = form_survival_base,
  data = data$surv_data_7,
  prior = prior_survival_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_base_7")
)
fit_survival_base_7 <- add_criterion(fit_survival_base_7, "loo")
```

@@

```{r, results="hide"}
fit_survival_base_28 <- brm(
  formula = form_survival_base,
  data = data$surv_data_28,
  prior = prior_survival_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_base_28")
)
fit_survival_base_28 <- add_criterion(fit_survival_base_28, "loo")
```

@@

fit_survival_time <- brm(
  formula = form_survival_time,
  data = data$surv_data_last_day,
  prior = prior_survival_time,
  inits = 0,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_time")
)
fit_survival_time <- add_criterion(fit_survival_time, "loo")
```

@@

fit_discharged_base <- brm(
  formula = form_discharged_base,
  data = data$patient_data,
  prior = prior_discharged_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_discharged_base")
)
fit_discharged_base <- add_criterion(fit_discharged_base, "loo")
```

@@

```{r, results="hide"}
fit_discharged_base_7 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_7,
  prior = prior_discharged_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_discharged_base_7")
)
fit_discharged_base_7 <- add_criterion(fit_discharged_base_7, "loo")
```

@@

```{r, results="hide"}
fit_discharged_base_28 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_28,
  prior = prior_discharged_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_discharged_base_28")
)
fit_discharged_base_28 <- add_criterion(fit_discharged_base_28, "loo")
```

@@

fit_discharged_time <- brm(
  formula = form_discharged_time,
  data = data$surv_data_last_day,
  prior = prior_discharged_time,
  inits = 0,
  control = list(adapt_delta = 0.98),
  file = paste0(cache_dir, "/fit_discharged_time")
)
fit_discharged_time <- add_criterion(fit_discharged_time, "loo")
```

@@

fit_outcome_base <- brm(
  formula = form_outcome_base,
  data = data$patient_data,
  prior = prior_outcome_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_outcome_base")
)
fit_outcome_base <- add_criterion(fit_outcome_base, "loo")
```

@@

```{r, results="hide"}
fit_outcome_base_7 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_7,
  prior = prior_outcome_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_outcome_base_7")
)
fit_outcome_base_7 <- add_criterion(fit_outcome_base_7, "loo")
```

@@

```{r, results="hide"}
fit_outcome_base_28 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_28,
  prior = prior_outcome_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_outcome_base_28")
)
fit_outcome_bas_28 <- add_criterion(fit_outcome_base_28, "loo")
```

@@

fit_worst_breathing_base <- brm(
  formula = form_worst_breathing_base,
  data = data$patient_data,
  prior = prior_worst_breathing_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_worst_breathing_base")
)
fit_worst_breathing_base <- add_criterion(fit_worst_breathing_base, "loo")
```

@@

```{r}
hypothesis_res_all <- do.call(rbind, hypothesis_res_list)
write_csv(hypothesis_res_all, path = here::here("manuscript/analysis_brms.csv"))
```
